A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-23 sections/Overview.tex
S2.5 one more example

@@

@@

Take the following worklist as an example
$$\al \Vdash \blue{(\lam x)~() \To_a a \le \al} , x:\al, \bt \Vdash \blue{\al \le \bt} \Vdash \blue{\bt \le 1}$$
A worklist is structurally a stack with its top element to the right.
There are three (blue-colored) judgment chains in the worklist,
where the first and second judgment chains are two subtyping judgments,
and the third judgment chain, $(\lam x)~() \To_a a \le \al$,
is a sequence of an inference judgment followed by a subtyping judgment.

>>>>

\jimmy{Some high level description for the structure}
A worklist is structurally a stack with its top element to the right.
$$\begin{aligned}
\text{Algorithmic judgement chain}\qquad&\jg &::=&\quad A \le B \mid e\Lto A \mid e\To_{a} \jg \mid \appInfAlg{A}{e}\\
\text{Algorithmic worklist}\qquad&\Gm &::=&\quad \nil \mid \Gm, a \mid \Gm, \al \mid \Gm, x: A \mid \Gm \Vdash \jg\\
\end{aligned}$$

@@

For example, the top judgment of the following worklist
checks the identity function against $\all a \to a$:
$$\Gm \Vdash \lam x \Lto \all a \to a$$
Then, two auxiliary variables $a$ and $x$ are introduced to help the type checking:
$$\Gm, a, x:a \Vdash x \Lto a$$
which will be satisfied after several steps, and the worklist becomes
$$\Gm, a, x:a$$
Since the variable declarations $a, x:a$ are only used for a judgment already processed,
they can be safely removed, leaving the remaining worklist $\Gm$ to be further reduced.

% $$\Gm \Vdash \all a \to a \le \all a \to a$$
% $$\Gm, a, \al \Vdash \al \to \al \le a \to a$$

@@

Take the following worklist as an example
$$\al \Vdash \blue{(\lam x)~() \To_a a \le \al} , x:\al, \bt \Vdash \blue{\al \le \bt} \Vdash \blue{\bt \le 1}$$
There are three (blue-colored) judgment chains in the worklist,
where the first and second judgment chains are two subtyping judgments,
and the third judgment chain, $(\lam x)~() \To_a a \le \al$,
is a sequence of an inference judgment followed by a subtyping judgment.
